Analyzing Toronto's Dining Scene: Public Food Safety and Economic Indicators in Focus

### 2024-01-25 Outputs_Folder/Paper/toronto_dinesafe_paper.qmd
Fixed typos and updated figure 3

@@

\section{Clean Dinesafe Dataset} 
\label{app:clean-dinesafe-dataset} 
Considering the huge content of the data set, this appendix contains a preview of the cleaned data set that has been used for the research. Original data is avaliable at https://github.com/ShadyEvan4830/Tonronto_Dinesafe_DataAnalysis.git
```{r}
#| echo: false
#| message: false
#| warning: false
# Load necessary libraries
library(readr)
library(dplyr)
library(knitr)
library(kableExtra)

@@

```
\clearpage
\section{Clean CPI Dataset} 
\label{app:clean-cpi-dataset} 
Considering the huge content of the data set, this appendix contains a preview of the cleaned data set that has been used for the research. Original data is avaliable at https://github.com/ShadyEvan4830/Tonronto_Dinesafe_DataAnalysis.git

>>>>

# Future Expectations
Although this report does not provide an in-depth analysis of Toronto's food safety situation and related economic indicators, the results of these studies provide some practical assistance for several future research avenues. Future investigations into food safety infraction behaviours' geographic and demographic distribution could reveal patterns and underlying inequalities across Toronto. Additionally, examining differences in infraction behaviour between different types of cuisine may provide insight into specific risk factors associated with food preparation practices. Finally, further exploring the relationship between economic recession and food safety compliance through comprehensive economic indicators rather than just CPI can provide a more detailed understanding of how economic pressure affects public health standards. The report believes these future studies will contribute to a more comprehensive understanding of food security in urban settings and inform more effective public health policies and interventions.

@@

\section{Clean Dinesafe Dataset} 
\label{app:clean-dinesafe-dataset} 
Considering the huge content of the data set, this appendix contains a preview of the cleaned data set that has been used for the research. Original data is avaliable at https://github.com/ShadyEvan4830/Toronto_Dinesafe_DataAnalysis.git
```{r}
#| echo: false
#| message: false
#| warning: false
# Load necessary libraries
library(readr)
library(dplyr)
library(knitr)
library(kableExtra)

@@

```
\clearpage
\section{Clean CPI Dataset} 
\label{app:clean-cpi-dataset} 
Considering the huge content of the data set, this appendix contains a preview of the cleaned data set that has been used for the research. Original data is avaliable at https://github.com/ShadyEvan4830/Toronto_Dinesafe_DataAnalysis.git
